---
title: "Assessment 1.1"
author: "Richard Laval Chung Wong Tsang s3876427"
date: "15/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
2. Create the heading of the first level and call it RMarkdown editing

# RMarkdown editing


3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)

**RMarkdown** is an authoring format that allows users to create high quality documents, reports, presentations and dashboards using languages such as R, Python and SQL. 

***RMarkdown*** allows you to create *data stories by narrating the data* written in an easy-to-write plain text format.

**RMarkdown** documents contain R code that are fully reproducible and can be exported in various formats such as html, pdf or MS Word. **RMarkdown** document in R contains *meta information* which is the header, *chunk of R code* and *mixed formatted text* such headers, bold, italics,  etc.

4. In the above use bold and italics for editing.

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html

[Markdown Basics - Lesson 8](https://rmarkdown.rstudio.com/lesson-8.html)


6. Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv

The name of the variable should be `fastfood`

```{r}
library(tidyverse)

fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

```

7. Display the first 10 rows of the dataset. Use Help to see how you can do this with `head()` function.
```{r}
head(fastfood,10)
```

8. Display the observations that has more than 1000 calories
```{r}
fastfood%>%
  filter(calories>1000)
```

9. Save observations with more than 40 in total_fat and more than 80 in total_carb in a new variable called `dont_eat_this`
```{r}
dont_eat_this<-fastfood%>%
  filter(total_fat>40 & total_carb>80)
```

10. Using the initial dataset variable, display observations from restaurant Mcdonalds
```{r}
fastfood%>%filter(restaurant=="Mcdonalds")
```